Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-08-10 Thesis/chapter/03-theoretical-background.tex
basic statistics + plotting

\textbf{Other statistics}
\begin{itemize}
    \item f-test 
    \item p-value 
    \item t-test
\end{itemize}

>>>>

\textbf{Other statistics}
\begin{itemize}
    \item f-test 
    \item p-value: Is the probability that a data point is observed under the null hypothesis. A small value argues against the null hypothesis. 
    \item t-test: will tell you if a variable is statistically significant. 
    \item f-test: will tell you if a group of variables is jointly significant
\end{itemize}

let's rule out different input variables: \\
does the heating temperature influence the resistance?  no \\
does the heating velocity influence the resistance?  hardly\\
do conc and layers number influence resistance? linear \\
do db velocity and db temperautre influence resistance? how\\

somebody very wise (my superviser) once said: we need to able to predict it otherwise it is just an engineering problem \td{(look at mail)}
